\chapter{Introduction}\label{ch:intro}

Not updated!

%\info{Overview of the paper: Problem / Challenge/issue / How analysed/solved / Transition to background}
There is wide acknowledgement and a broad literature reporting a widening gap between science and its relevant policy (e.g. \cite{Nau2009,EdlerKB2022}\improvement{I have better refs for this}). Possibly the most stark example of this gap is between climate and nature (CAN) science and policy; Despite decades of scientists' warnings of catastrophic outcomes of climate change and biodiversity loss, the gap - for example, the difference between levels of atmospheric greenhouse gases (GHGs) and policy to reduce those GHGs\footnote{Measures of GHG volumes are useful for monitoring human impact on climate but, as \textcite{MorenoSF2016} argue, this is a narrow measure of our impact on the natural world and risks perpetuating and exacerbating societal and global injustices.} - continues to widen (\cite{StoddardEtAl2021,IPBES2022,IPCC2023}). This gap between settled science and policy ambition is wide enough to threaten the survival of ecosystems (\cite{DiazEtAl2019,IPBES2022}), global security (\cite{WEF2024}), human civilisation (\cite{TschakertEAKO2019}) and, potentially, the future of humanity (\cite{McKayEtAl2022}). With so much at stake, it is essential that all parties at the CAN policy interface are effective in their roles. Thus, scholars have developed theory around the roles for scientists at the interface with policy, and recommended how they may improve their engagement. These theories are founded studies of the needs of policy which consider how knowledge flows from science into decision-making and where these knowledge flows may be interrupted. 

%\info{Background - Origins of problem - Economic, social, political, and/or technical factors at play - What previous analyses tell us about problem - transition to current}
The traditional ``linear'' model of policy-making is that ``knowledge shapes policy'' that is, knowledge is produced by science and this informs policy (\cite{Pielke2007}, p12-3; \cite{BoswellS2017}). In reality, policy-making can be much messier as a consequence of the complexity of policy problems (\cite{Cairney2016}), the contrasting ``cultures'' of science and policy (\cite{Dale2002,Obermeister2022}), and the competing influences of political and commercial interests (\cite{StoddardEtAl2021}). Recognising this messier reality, and the frustrations of scientists and policymakers at the interface, \textcite{Pielke2007} defined idealised roles for scientists at the interface, which have been further developed over recent years (e.g. \cite{RapleyD2014,GluckmanBK2021,GregoryBW2024}). Others, having studied the needs of policy the interface, have made recommendations for scientists, including improving their communication, their knowledge of policy processes, the relevance of their research, and the synthesis of evidence (\cite{KennyRHTB2017,LubchencoR2020,GluckmanBK2021,Bisbal2024}). To remain credible\improvement{Cash et al. 2003 CRELE is relevant here}, scientists are also held to high standards of transparency, integrity and legitimacy (\cite{KennyRHTB2017,ColognaKMBMO2024,GregoryBW2024}). There is great emphasis on the actions and roles that scientists \emph{should} assume, but this neglects to understand the actions and roles that scientists already \emph{do} assume and their real-world experiences at the CAN policy interface.

%\info{Challenge and Issues: - Current challenge/issue being addressed - Why different from background - What makes this challenge/issue analysis different - Transition from what contributes to analysis to how conducted}
Little work exists to understand what are the experiences of scientists engaged in policy (\cite{KennyRHTB2017}) or what they have learned (with the exception of \cite{Obermeister2022}). The roles played by scientists when engaging with policy are tempered by the contexts, such as the field of science and nature of the policy, within which they engage (\cite{EdlerKB2022}). With CAN-related policy, this context is mutlifaceted, involving a range of scientific fields, approaches and outcomes; policy issues and policy settings; and wider factors such as political and commercial perspectives. However, current analyses tend to assume homogeneity across all science-policy contexts. It is perhaps unreasonable to prescribe the actions and roles that scientists should assume without first understanding what are their experiences of the CAN policy interface. Moreover, there is potentially a great deal to learn from scientists who have engaged with policy both from their perceived successes and their frustrations. Therefore, this thesis takes a step back from current works that place the onus of policy impact and influence on scientists. Instead, it uses the insights of scientists themselves to understand how the CAN interface can be enhanced by scientists and by policymakers\unsure{hopefully not too ambitious}.

%\info{How Analysis Was Conducted and Summary of Results - How was the analysis conducted (integration of framework, cases, and/or conceptual framework) - Summarize interesting points in the analysis - Summarize conclusions - Transition to how we got here (Roadmap)}
In this study, scientists are interviewed about their real-world experiences at the CAN policy interface to discover the actions they take to ease the flow of knowledge into policy. Using the Individual-Social-Material framework of \textcite{DarntonH2013}, it reflects on the factors that influence the behaviours of scientists when they have engaged with CAN policy. It further considers how these behaviours match with the roles prescribed for scientists at the policy interface and inductively contextualises these engagements to understand how and why roles and experiences differ from from prescribed roles and from each other. This study finds [\#\info{\# - indicates text to be completed later}\emph{some interesting points}\#] and draws [\#\emph{some conclusions}\#]. 

This study brings some balance to the discussion of roles at the policy interface by spotlighting the real-world experience and learning of scientists in a particularly challenging arena - that of CAN policy. It provides descriptive insights to a largely normative literature about scientists' roles in policy-making. In so doing it offers [\#advice\# / \#reflection\# / \#solace\#] to scientists and [\#insights\# / \#recommendations\# / \#appeals\#] to policymakers, which are intended to support the shared aim of science and policy to enhance how knowledge flows through the CAN policy interface.

bracketing - \cite{CreswellP2017}
It is pertinent in all [such studies] to include a note on the researcher's positionality [refs]. I identify myself as a broad-[spectrum] scientist, having studied environmental sciences, focussing on monitoring the land- and sea-scape using remote sensing. I have spent more than 2 decades focussed on developing algorithms for processing aerial imagery. Much of that time, I worked with neural network algorithms, including introducing deep learning to an arms length government organisation, whilst all the time maintaining a passion for, and occasional activism about, the natural world. The present study emerged out of the mismatch I directly perceived between scientific understanding, both regarding the natural world and technological issues (particularly regarding so-called ``artificial intelligence''), and public decision making.

\#\emph{paragraph introducing each chapter}\#

%characteristics of the interface that scientists encounter.

%applied to \# semi-structured interviews. I 

%this study aims to understand the roles they have played and the contexts within which they engaged.

My work is consciously vague about policy much as many other studies are vague about science